Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-20 VMCAI-revised-version/final.tex
u

% Hence we can see how adding transitions can 
% turn a system that is not bounded resilient into one that is. 
% \alain{à quoi sert cette remarque ?}

@@

\begin{proposition}\label{srp down up}
{\sc State-resilience} is undecidable for $\post$-ideal-effective ???? and $\pred$-basis-effective $\omega^2$-WSTS with strong compatibility
when
$\Safe=\mathop{\downarrow} \Safe$.
\end{proposition}

>>>>

\mathieu{Reviewer 1: we can consider that the example at the bottom of page 8, even if it is a WSTS, is a very particular case very different from VASS, lossy counter, Petri nets, communicating automata, etc. and wonder if classes containing such  systems are interesting per se. }
% Hence we can see how adding transitions can 
% turn a system that is not bounded resilient into one that is. 
% \alain{à quoi sert cette remarque ?}

@@

\begin{proposition}\label{srp down up}
{\sc State-resilience} is undecidable for 
%$\post$-ideal-effective ???? and
 $\pred$-basis-effective $\omega^2$-WSTS with strong compatibility
when
$\Safe=\mathop{\downarrow} \Safe$.
\end{proposition}
